---
title: "S18813_mini_project_2"
author: "S/18/813"
date: "2024-05-30"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### importing the packages
```{r}
library(tidyverse)
require(ggplot2)
require(GGally)
require(CCA)
require(CCP)
```

### Loading the datasets
```{r}
bioData <- read_csv("../Data/bioData.csv")
chemData <- read_csv("../Data/chemData.csv")
```

### Viewing Two 
```{r}
head(bioData)
head(chemData)
```

### Combining two data set
```{r}
mergedData <- merge(bioData, chemData, by = "Kod_Canoco")
```

```{r}
head(mergedData)
```

### Renaming Dataset
```{r}
old_names <- c("Kod_Canoco", "SaprInd", "Lital", "RETI", "EPTAbu", "Marg", "Metaritr",
               "JepAbu", "Epiritral", "Hyporitral", "Ntaxon", "Nceled", "Bindex", "EPTTax",
               "PosAbu", "Spasaci", "MDS_1", "MDS_2", "Tepl_max", "%O2", "BSK5", "Kond",
               "N-NH4", "N-NO3", "Pcelk")
new_names <- c("Site_Code", "Saprobic_Index", "Littoral_Abundance", "Retention_Index", 
               "EPT_Abundance", "Margalef_Index", "Metarhithral_Abundance", "Jep_Abundance", 
               "Epiritral_Abundance", "Hyporitral_Abundance", "Number_of_Taxa", "Number_of_Cephalopods",
               "Biotic_Index", "EPT_Taxa", "Positive_Abundance", "Spasaci_Index", "MDS_1", "MDS_2",
               "Max_Temperature", "Oxygen_Percentage", "Biochemical_Oxygen_Demand", "Conductivity",
               "Ammonium_Nitrogen", "Nitrate_Nitrogen", "Total_Phosphorus")

colnames(mergedData) <- new_names[match(colnames(mergedData), old_names)]

```

```{r}
head(mergedData)
```
### Selecting subset
```{r}
bio <- mergedData[,2:8]
chem <- mergedData[,19:23]
```

### Correlation plot for bio data
```{r}
ggpairs(bio)
```

### Correlation plot for chem data
```{r}
ggpairs(chem)
```

```{r}
matcor(bio, chem)
```

##Canonical Correlation Analysis

### Canonical Correlations
```{r}
cc1 <- cc(bio, chem)
cc1$cor

```
### Canonical Coefficients
```{r}
cc1[3:4]
```

### Canonical Loadings
```{r}
cc2 <- comput(bio, chem, cc1)
cc2[3:6]
```

### Tests Of Canonical Dimension
```{r}
rho <- cc1$cor

n <- dim(bio)[1] # number of observations
p <- length(bio) # number of variables in first set
q <- length(chem)  # number of variables in the second set
```

#### Wilks Test
```{r}
p.asym(rho, n, p, q, tstat = "Wilks")
```

#### Hotelling Test
```{r}
p.asym(rho, n, p, q, tstat = "Hotelling")
```

#### Pillai Test
```{r}
p.asym(rho, n, p, q, tstat = "Pillai")
```

#### Roy Test
```{r}
p.asym(rho, n, p, q, tstat = "Roy")
```
### standardized bio canonical coefficients
```{r}
s1 <- diag(sqrt(diag(cov(bio))))
s1 %*% cc1$xcoef
```

### standardized chem canonical coefficients
```{r}
s2 <- diag(sqrt(diag(cov(chem))))
s2 %*% cc1$ycoef
```

